An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-04-08 mixedwindow.tex
Remove hyphen in pseudo-true

In this paper, I show that a modified version of their statistic is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, we need a consistent estimate of the pseudo-true
benchmark model, while maintaining an inconsistent estimate of the
larger model so that we can ignore nesting.  We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I will present the
single-comparison statistic first and then extend it to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If the linear model is
correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value%
\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} %
and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

>>>>

In this paper, I show that a modified version of their statistic is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, we need a consistent estimate of the pseudotrue
benchmark model, while maintaining an inconsistent estimate of the
larger model so that we can ignore nesting.  We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I will present the
single-comparison statistic first and then extend it to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If the linear model is
correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value%
\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} %
and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}
